LWE Trapdoor One-Way Function

### 2017-06-30 latex/qtpie/paper.tex
added more key agreement ideas

\todototoc
\listoftodos

>>>>

\todototoc
\listoftodos
You are missing all the non fake signature etc.

Where is your trap door function defined where is the key exchange defined ?

You should use the environment algorithm to write your algorithm. It is difficult to understand as is.

Section 2 is too short to be a section as is.

Addition over what field ? Etc for the rest. (edited)

Why 800 bits for N. Why not less ?

Given the following function....
That's not a function. That's an equation. (edited)

What are p q e ?

Use leftarrow instead of :=

If it's an algorithm don't put equivalent (triple equal) in it

Use $p^-1$ or something else but not pi.
It confusing.

Inverse mod N in which field ?????
Or group.
My bad it's in 2.

Basic concept is not a good name for a section.
Use specifications.
Or Design motivation (after specifications)

You should not need to specify mod N in each operations.

Why k private is 520 bits ?

How does all this compares to others methods ?

What is that t in key recovery.
